Galois Transformers and Modular Abstract Interpreters

### 2015-03-26 writeup/oopsla2015.tex
killed a comma

The present version of this paper has aimed to clarify the novelty of
this work and explain how, while the idea of ``going from monads to
monad transformers'' is in some sense an obvious idea, there is no way
to get there from the PLDI'13 paper of Sergey et al., without
significant research.  That research is the subject of this paper.

>>>>

The present version of this paper has aimed to clarify the novelty of this work
and explain how, while the idea of ``going from monads to monad transformers''
is in some sense an obvious idea, there is no way to get there from the PLDI'13
paper of Sergey et al. without significant research. That research is the
subject of this paper.
